Argumentation theory for mathematical argument\thanks{Support from the UK Engineering and Physical Sciences Research Council is acknowledged under grants EPSRC EP/K040251/2 (Corneli, Martin and Nesin), EP/J017728/2 (Murray-Rust) and EP/P017320/1 (Pease).}

### 2018-07-11 main.tex
fix bracket

\paragraph{IATC allows the argumentation aspects of mathematical dialogues to be represented as explicit graphical structures, which gives a plausible basis from which to develop an explicit computational model of the reasoning steps that are implied in mathematical argumentation.}
\paragraph{\citet{corneli2017towards} showed how IATC could be used to create graphical models of the discussion that develops around a question posted on MathOverflow.  Here we will remark further on implications for computational modelling.
The question, which was given the title  ``Group cannot be the union of conjugates'' \cite{chandrasekhar2010group} is as follows:

>>>>

\paragraph{IATC allows the argumentation aspects of mathematical dialogues to be represented as explicit graphical structures, which gives a plausible basis from which to develop an explicit computational model of the reasoning steps that are implied in mathematical argumentation.}
\paragraph{\citet{corneli2017towards} showed how IATC could be used to create graphical models of the discussion that develops around a question posted on MathOverflow.}  Here we will remark further on implications for computational modelling.
The question, which was given the title  ``Group cannot be the union of conjugates'' \cite{chandrasekhar2010group} is as follows:
